Wired for Success: Sweden's Electrical Innovators in the Age of Industrial Transformation

### 2023-05-15 index.qmd
change colours

# Create the ggplot visualization
ggplot(books, aes(x = records, y = name, fill = factor(volume))) +
  geom_col(alpha = .8) +
  labs(x = "Number of biographies", y = "Book volume",
  title = "Number of biographies in Vem är Vem?",
  fill = "Edition") +
  scale_x_continuous(labels = scales::number_format()) +
  scale_fill_manual(values = c("#00AFBB", "#E7B800"))

@@

timeline <- tibble(
  event = c("Birth", "Graduated from Bergsskolan in Filipstad", 
            "Specialized studies at the Royal Institute of Technology (KTH)",
            "Studied at the Institute of Metallurgy and Stockholm University",
            "Marriage to Sigrid Johansson",
            "Birth of Ingvar", "Birth of Lennart",
            "Chemist at Strömsnäs Järnverks A-B in Degerfors",
            "Metallurgist and chemist at Westinghouse Electric & Manufacturing Co.",
            "Chief metallurgist at Laclede Steel Co. in Alton, Illinois, USA",
            "Furnace and steelworks engineer at A-B Iggesunds Bruk",
            "Site manager at Gunnebo Bruks Nya A-B, Varbergsverket",
            "Member of the municipal executive committee",
            "Deputy chairman of the economic department",
            "Deputy member of the board of the power plant",
            "Chairman of Varbergs Sparbank",
            "Employer representative in the district council of the county labor board",
            "Member of the board of Varbergs Luftskyddsförening",
            "Secretary of Varbergs Högerförening",
            "Chairman of the railway sick fund",
            "Plant Society for Small Bird Friends",
            "Traveled to Germany",
            "Traveled to Denmark and Czechoslovakia",
            "Traveled to Austria",
            "Traveled to the USA",
            "*Wrote 'Some fundamental factors for obtaining sharp thermal curves'",
            "*Wrote 'Contemporary production of saw blades, circular saws, and machine knives'",
            "Hobbies: hunting and fishing"
  ),
  start_year = c(1893, 1917, 1920, 1921, 1936, 1938, 1942, 1918, 1923, 1927, 1929,
                 1931, NA, NA, NA, NA, NA, NA, NA, NA, NA, 1921, 1921, 1921, 1923, 1925, 1931, NA),
  end_year = c(1893, 1917, 1922, 1922, NA, NA, NA, 1920, 1929, 1927, 1931,
               NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 1923, 1923, 1921, 1929, NA, NA, NA)
)

>>>>

# Create the ggplot visualization
ggplot(books, aes(x = records, y = name, fill = factor(volume))) +
  geom_col(alpha = .8) +
  labs(x = "Number of biographies", y = "Book volume",
  title = "Number of biographies in Vem är Vem?",
  fill = "Edition") +
  scale_x_continuous(labels = scales::number_format()) +
  scale_fill_manual(values = c("#2B8CBE", "#be5d2b"))

@@

timeline <- tibble(
  event = c("Birth", "Graduated from Bergsskolan in Filipstad", 
            "Specialized studies at the Royal Institute of Technology (KTH)",
            "Studied at the Institute of Metallurgy and Stockholm University",
            "Marriage to Sigrid Johansson",
            "Birth of Ingvar", "Birth of Lennart",
            "Chemist at Strömsnäs Järnverks A-B in Degerfors",
            "Metallurgist and chemist at Westinghouse Electric & Manufacturing Co.",
            "Chief metallurgist at Laclede Steel Co. in Alton, Illinois, USA",
            "Furnace and steelworks engineer at A-B Iggesunds Bruk",
            "Site manager at Gunnebo Bruks Nya A-B, Varbergsverket",
            "Member of the municipal executive committee",
            "Deputy chairman of the economic department",
            "Deputy member of the board of the power plant",
            "Chairman of Varbergs Sparbank",
            "Employer representative in the district council of the county labor board",
            "Member of the board of Varbergs Luftskyddsförening",
            "Secretary of Varbergs Högerförening",
            "Chairman of the railway sick fund",
            "Plant Society for Small Bird Friends",
            "Traveled to Germany",
            "Traveled to Denmark and Czechoslovakia",
            "Traveled to Austria",
            "Traveled to the USA",
            "*Wrote 'Some fundamental factors for obtaining sharp thermal curves'",
            "*Wrote 'Contemporary production of saw blades, circular saws, and machine knives'",
            "Hobbies: hunting and fishing"
  ),
  start_year = c(1893, 1917, 1920, 1921, 1936, 1938, 1942, 1918, 1923, 1927, 1929,
                 1931, NA, NA, NA, NA, NA, NA, NA, NA, NA, 1921, 1921, 1921, 1923, 1925, 1931, NA),
  end_year = c(1893, 1917, 1922, 1922, 1936, 1938, 1942, 1920, 1929, 1927, 1931,
               NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 1923, 1923, 1921, 1929, NA, NA, NA)
)
